

```{r}




library("lubridate")
library("ncdf4")
library("zoo")
library("Rsenal")
library("humidity")



```
Line#
Date
Wind Direction (S-WDA 20137625:10085790-1), *, Otjiwarongo_ESE28km
Solar Radiation (S-LIB 20137625:10085812-1), W/m^2, Otjiwarongo_ESE28km
Temperature (S-THB 20137625:10087651-1), *C, Otjiwarongo_ESE28km
RH (S-THB 20137625:10087651-2), %, Otjiwarongo_ESE28km
Dew Point (S-THB 20137625:10087651-3), *C, Otjiwarongo_ESE28km
Pressure (S-BPB 20137625:10090141-1), mbar, Otjiwarongo_ESE28km
Wind Speed (S-WSA 20137625:10090349-1), m/s, Otjiwarongo_ESE28km
Gust Speed (S-WSA 20137625:10090349-2), m/s, Otjiwarongo_ESE28km
Battery (RX3000 BATTERY 20137625:20137625-B), V, Otjiwarongo_ESE28km


Wind Direction (S-WDA 20137625:10085790-1), *, Ojiwarango_ESE28km
Solar Radiation (S-LIB 20137625:10085812-1), W/m^2, Ojiwarango_ESE28km
Temperature (S-THB 20137625:10087651-1), *C, Ojiwarango_ESE28km
RH (S-THB 20137625:10087651-2), %, Ojiwarango_ESE28km
Dew Point (S-THB 20137625:10087651-3), *C, Ojiwarango_ESE28km
Pressure (S-BPB 20137625:10090141-1), mbar, Ojiwarango_ESE28km
Wind Speed (S-WSA 20137625:10090349-1), m/s, Ojiwarango_ESE28km
Gust Speed (S-WSA 20137625:10090349-2), m/s, Ojiwarango_ESE28km
Battery (RX3000 BATTERY 20137625:20137625-B), V, Ojiwarango_ESE28km


fields to remove

Wind Direction (S-WDA 20137625:10085790-1), *, Ojiwarango_ESE28km
Solar Radiation (S-LIB 20137625:10085812-1), W/m^2, Ojiwarango_ESE28km
Temperature (S-THB 20137625:10087651-1), *C, Ojiwarango_ESE28km
RH (S-THB 20137625:10087651-2), %, Ojiwarango_ESE28km
Dew Point (S-THB 20137625:10087651-3), *C, Ojiwarango_ESE28km
Pressure (S-BPB 20137625:10090141-1), mbar, Ojiwarango_ESE28km
Wind Speed (S-WSA 20137625:10090349-1), m/s, Ojiwarango_ESE28km
Gust Speed (S-WSA 20137625:10090349-2), m/s, Ojiwarango_ESE28km
Battery (RX3000 BATTERY 20137625:20137625-B), V, Ojiwarango_ESE28km

```{r}


csv_file  = "~/GitHub/HOBOLINK/April_2018_2018_05_10_19_29_55_UTC_1.csv"

site_label     = "Ojiwarango ESE28km"
site_latitude  = - ( 20 + (34.0 + 32.69 /60.0) / 60.0 )
site_longitude =   ( 16 + (53.0 + 20.79 /60.0) / 60.0 )
site_altitude  =  1607.0

start_window = "2018-04-01_00:00:00"
end_window   = "2018-04-30_23:59:00"


input_directory = "~/GitHub/HOBOLINK/"
csv_file        = paste(input_directory,
                        "Ojiwarango_ESE28km_2018-04-01_00:00:00_2018.csv",
                        sep="")

ncdf_file    = paste(input_directory,
                     "Ojiwarango_ESE28km_",
                     start_window,
                     "_",
                     end_window,
                     ".csv",
                     sep = "")


start_time = as.POSIXct(x      = paste(gsub(pattern     = "_", 
                                            replacement = " ", 
                                            x           = start_window),
                                       "UTC",
                                       sep=" "), 
                        format = "%Y-%m-%d %H:%M:%S",
                        tz     = "UTC",
                        origin = "1970-01-01 00:00:00 UTC")

end_time   = as.POSIXct(x      = paste(gsub(pattern     = "_", 
                                            replacement = " ", 
                                            x           = end_window),
                                       "UTC",
                                       sep=" "), 
                        format = "%Y-%m-%d %H:%M:%S",
                        tz     = "UTC",
                        origin = "1970-01-01 00:00:00 UTC")

time       = seq(from = start_time, 
                 to   = end_time,
                 by   = 60.0)

data = read.csv(file = csv_file, 
                header = TRUE, 
                quote = "\"",
                dec = ".", 
                fill = TRUE,
                comment.char = "")

remove(csv_file)


names(data)[ 1] = "Record"
names(data)[ 2] = "time"
names(data)[ 3] = "wind_from_direction"
names(data)[ 4] = "solar_irradiance"
names(data)[ 5] = "relative_humidity"
names(data)[ 6] = "air_temperature"
names(data)[ 7] = "dew_point_temperature"
names(data)[ 8] = "air_pressure"
names(data)[ 9] = "wind_speed"
names(data)[10] = "wind_speed_of_gust"
names(data)[11] = "Battery_Voltage"

data$wind_from_direction   = as.numeric(data$wind_from_direction)
data$solar_irradiance      = as.numeric(data$solar_irradiance)
data$relative_humidity     = as.numeric(data$relative_humidity)
data$air_temperature       = as.numeric(data$air_temperature)
data$dew_point_temperature = as.numeric(data$dew_point_temperature)
data$air_pressure          = as.numeric(data$air_pressure)
data$wind_speed            = as.numeric(data$wind_speed)
data$wind_speed_of_gust    = as.numeric(data$wind_speed_of_gust)
data$Battery_Voltage       = as.numeric(data$Battery_Voltage)

deleteme = wdws2uv(wd = data$wind_from_direction, 
                   ws = data$wind_speed)

data$eastward_wind         = deleteme[,1]
data$northward_wind        = deleteme[,2]


data$specific_humidity = SH(e = SVP(t       = data$air_temperature,
                                    isK     = FALSE,
                                    formula = "Clausius-Clapeyron"),
                            p = data$air_pressure * 100.0)

remove(deleteme)

zoo.time = as.POSIXct(x      = strptime(data$time, "%y/%m/%d %H:%M:%S"), 
                      format = "%Y-%m-%d %H:%M:%S",
                      tz     = "UTC",
                      origin = "1970-01-01 00:00:00 UTC")

keeps = names(data)[ 3:11]
data  = data[keeps]
remove(keeps)


zoo.data = as.zoo(x        = data,
                  order.by = zoo.time)

remove(data)


zoo.data =  merge.zoo(x = zoo.data, 
                      y = zoo(x        = ,
                              order.by = time), 
                      fill = NA)

```




```{r}


  netcdf_output_file_name = paste(file_title_string,
                                  ".nc",
                                  sep="")

  netcdf_time_dim  = ncdim_def(name  = "time",
                               units = "days since 1970-01-01 00:00:00",
                               val   = Days_from_1970_01_01,
                               unlim = TRUE,
                               calendar="standard")

  netcdf_name_dim  = ncdim_def(name  = "name_strlen",
                               units = "",
                               val   = 1:nchar(file_title_string),
                               unlim = FALSE,
                               create_dimvar=FALSE)




  fill_value = 9.96921e+36


  netcdf_stn = ncvar_def(nam      = "station_name",
                         units    = "",
                         dim      = netcdf_name_dim,
                         longname = "station name",
                         prec     = "char")


  netcdf_lat = ncvar_def(nam      = "latitude",
                         units    = "degrees_north",
                         dim      = list(),
                         longname = "Latitude",
                         prec     = "single")

  netcdf_lon = ncvar_def(nam      = "longitude",
                         units    = "degrees_east",
                         dim      = list(),
                         longname = "Longitude",
                         prec     = "single")

  netcdf_alt = ncvar_def(nam      = "altitude",
                         units    = "m",
                         dim      = list(),
                         longname = "Elevation",
                         prec     = "single")


  netcdf_available_variables = list(netcdf_lat,
                                    netcdf_lon,
                                    netcdf_alt,
                                    netcdf_stn)


  if ("TMAX" %in% available_datafields) {
    netcdf_tmax = ncvar_def(nam      = "maximum_air_temperature",
                            units    = "degC",
                            dim      = netcdf_time_dim,
                            missval  = fill_value,
                            longname = "2-m Maximum Daily Air Temperature",
                            prec     = "single")
    netcdf_available_variables = list.append(netcdf_available_variables,
                                             netcdf_tmax)
  }

  if ("TMIN" %in% available_datafields) {
    netcdf_tmin = ncvar_def(nam      = "minimum_air_temperature",
                            units    = "degC",
                            dim      = netcdf_time_dim,
                            missval  = fill_value,
                            longname = "2-m Minimium Daily Air Temperature",
                            prec     = "single")
    netcdf_available_variables = list.append(netcdf_available_variables,
                                             netcdf_tmin)
  }


  if ("TAVG" %in% available_datafields) {
    netcdf_tavg = ncvar_def(nam      = "mean_air_temperature",
                            units    = "degC",
                            dim      = netcdf_time_dim,
                            missval  = fill_value,
                            longname = "2-m Mean Daily Air Temperature",
                            prec     = "single")
    netcdf_available_variables = list.append(netcdf_available_variables,
                                             netcdf_tavg)
  }

  if ("PRCP" %in% available_datafields) {
    netcdf_prcp = ncvar_def(nam      = "precipitation_amount",
                            units    = "kg m-2",
                            dim      = netcdf_time_dim,
                            missval  = fill_value,
                            longname = "Daily Total Precipitation",
                            prec     = "single")
    netcdf_available_variables = list.append(netcdf_available_variables,
                                             netcdf_prcp)
  }

  if ("SNOW" %in% available_datafields) {
    netcdf_snow = ncvar_def(nam      = "thickness_of_snowfall_amount",
                            units    = "m",
                            dim      = netcdf_time_dim,
                            missval  = fill_value,
                            longname = "Daily Total Snowfall",
                            prec     = "single")
    netcdf_available_variables = list.append(netcdf_available_variables,
                                             netcdf_snow)
  }

  if ("SNWD" %in% available_datafields) {
    netcdf_snwd = ncvar_def(nam      = "surface_snow_thickness",
                            units    = "m",
                            dim      = netcdf_time_dim,
                            missval  = fill_value,
                            longname = "Snow Depth on Surface",
                            prec     = "single")
    netcdf_available_variables = list.append(netcdf_available_variables,
                                             netcdf_snwd)
  }


  if ("WESD" %in% available_datafields) {
    netcdf_wesd = ncvar_def(nam      = "liquid_water_content_of_surface_snow",
                            units    = "kg m-2",
                            dim      = netcdf_time_dim,
                            missval  = fill_value,
                            longname = "Liquid Snow Water Equivalent Depth on Surface",
                            prec     = "single")
    netcdf_available_variables = list.append(netcdf_available_variables,
                                             netcdf_wesd)
  }

  if ("WESF" %in% available_datafields) {
    netcdf_wesf = ncvar_def(nam      = "liquid_water_equivalent_snowfall_amount",
                            units    = "kg m-2",
                            dim      = netcdf_time_dim,
                            missval  = fill_value,
                            longname = "Liquid Snow Water Equivalent Depth on Surface",
                            prec     = "single")
    netcdf_available_variables = list.append(netcdf_available_variables,
                                             netcdf_wesf)
  }


  if ("AWND" %in% available_datafields) {
    netcdf_awnd = ncvar_def(nam      = "mean_wind_speed",
                            units    = "m s-1",
                            dim      = netcdf_time_dim,
                            missval  = fill_value,
                            longname = "Mean Daily Wind Speed",
                            prec     = "single")
    netcdf_available_variables = list.append(netcdf_available_variables,
                                             netcdf_awnd)
  }


  if ("AWNDR" %in% available_datafields) {
    netcdf_awdr = ncvar_def(nam      = "mean_wind_from_direction",
                            units    = "degrees_from",
                            dim      = netcdf_time_dim,
                            missval  = fill_value,
                            longname = "Mean Daily Wind Origin Direction",
                            prec     = "single")
    netcdf_available_variables = list.append(netcdf_available_variables,
                                             netcdf_awdr)
  }








  nc_ghcn = nc_create(filename = netcdf_output_file_name,
                        vars     = netcdf_available_variables,
                        force_v4 = FALSE,
                        verbose  = FALSE )






ncatt_put(nc         = nc_ghcn,
          varid      = 0,
          attname    = "Title",
          attval     = paste("NCEI Data Hourly Output for ",
                             station_name_label,
                             sep=""),
          prec       = NA,
          verbose    = FALSE,
          definemode = FALSE )

ncatt_put(nc         = nc_ghcn,
          varid      = 0,
          attname    = "GHCN_Station_Code",
          attval     = ncdc_id_code,
          prec       = NA,
          verbose    = FALSE,
          definemode = FALSE )

ncatt_put(nc         = nc_ghcn,
          varid      = 0,
          attname    = "Station_Name",
          attval     = station_name_label,
          prec       = NA,
          verbose    = FALSE,
          definemode = FALSE )

ncatt_put(nc         = nc_ghcn,
          varid      = 0,
          attname    = "Station_Latitude",
          attval     = station_latitude,
          prec       = NA,
          verbose    = FALSE,
          definemode = FALSE )

ncatt_put(nc         = nc_ghcn,
          varid      = 0,
          attname    = "Station_Longitude",
          attval     = station_longitude,
          prec       = NA,
          verbose    = FALSE,
          definemode = FALSE )

ncatt_put(nc         = nc_ghcn,
          varid      = 0,
          attname    = "Station_Elevation_in_Meters",
          attval     = station_altitude,
          prec       = NA,
          verbose    = FALSE,
          definemode = FALSE )

ncatt_put(nc         = nc_ghcn,
          varid      = 0,
          attname    = "featureType",
          attval     = "timeSeries",
          prec       = NA,
          verbose    = FALSE,
          definemode = FALSE)

ncatt_put(nc         = nc_ghcn,
           varid      = 0,
           attname    = "Conventions",
           attval     = "CF-1.6",
           prec       = NA,
           verbose    = FALSE,
           definemode = FALSE)


  ncatt_put(nc         = nc_ghcn,
            varid      = netcdf_stn,
            attname    = "description",
            attval     = "station name",
            prec       = NA,
            verbose    = FALSE,
            definemode = FALSE )

   ncatt_put(nc         = nc_ghcn,
             varid      = netcdf_stn,
             attname    = "cf_role",
             attval     = "timeseries_id",
             prec       = NA,
             verbose    = FALSE,
             definemode = FALSE )


  ncatt_put(nc         = nc_ghcn,
            varid      = netcdf_alt,
            attname    = "standard_name",
            attval     = "altitude",
            prec       = NA,
            verbose    = FALSE,
            definemode = FALSE )

   ncatt_put(nc         = nc_ghcn,
             varid      = netcdf_alt,
             attname    = "positive",
             attval     = "up",
             prec       = NA,
             verbose    = FALSE,
             definemode = FALSE )

  ncatt_put(nc         = nc_ghcn,
            varid      = netcdf_alt,
            attname    = "description",
            attval     = "Elevation",
            prec       = NA,
            verbose    = FALSE,
            definemode = FALSE )

  ncatt_put(nc         = nc_ghcn,
            varid      = netcdf_lon,
            attname    = "standard_name",
            attval     = "longitude",
            prec       = NA,
            verbose    = FALSE,
            definemode = FALSE )

  ncatt_put(nc         = nc_ghcn,
            varid      = netcdf_lon,
            attname    = "description",
            attval     = "Longitude",
            prec       = NA,
            verbose    = FALSE,
            definemode = FALSE )

  ncatt_put(nc         = nc_ghcn,
            varid      = netcdf_lat,
            attname    = "standard_name",
            attval     = "latitude",
            prec       = NA,
            verbose    = FALSE,
            definemode = FALSE )

  ncatt_put(nc         = nc_ghcn,
            varid      = netcdf_lat,
            attname    = "description",
            attval     = "Latitude",
            prec       = NA,
            verbose    = FALSE,
            definemode = FALSE )



  if ("TMAX" %in% available_datafields) {
      ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_tmax,
              attname    = "standard_name",
              attval     = "air_temperature",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

      ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_tmax,
              attname    = "cell_methods",
              attval     = "time: maximum",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

      ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_tmax,
              attname    = "description",
              attval     = "2-m Minimium Daily Air Temperature",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

      ncatt_put(nc         = nc_ghcn,
         varid      = netcdf_tmax,
         attname    = "coordinates",
         attval     = "time latitude longitude altitude station_name",
         prec       = NA,
         verbose    = FALSE,
         definemode = FALSE )

  }

  if ("TMIN" %in% available_datafields) {
    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_tmin,
              attname    = "standard_name",
              attval     = "air_temperature",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_tmin,
              attname    = "cell_methods",
              attval     = "time: minimum",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_tmin,
              attname    = "description",
              attval     = "2-m Minimium Daily Air Temperature",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )


     ncatt_put(nc         = nc_ghcn,
        varid      = netcdf_tmin,
        attname    = "coordinates",
        attval     = "time latitude longitude altitude station_name",
        prec       = NA,
        verbose    = FALSE,
        definemode = FALSE )
  }

  if ("TAVG" %in% available_datafields) {
    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_tavg,
              attname    = "standard_name",
              attval     = "air_temperature",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_tavg,
              attname    = "cell_methods",
              attval     = "time: mean",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_tavg,
              attname    = "description",
              attval     = "2-m Mean Daily Air Temperature",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

      ncatt_put(nc         = nc_ghcn,
                varid      = netcdf_tmax,
                attname    = "coordinates",
                attval     = "time latitude longitude altitude station_name",
                prec       = NA,
                verbose    = FALSE,
                definemode = FALSE )
  }




  if ("PRCP" %in% available_datafields) {
    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_prcp,
              attname    = "standard_name",
              attval     = "precipitation_amount",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_prcp,
              attname    = "cell_methods",
              attval     = "time: sum",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_prcp,
              attname    = "description",
              attval     = "Daily Total Precipitation",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

      ncatt_put(nc         = nc_ghcn,
               varid      = netcdf_prcp,
               attname    = "coordinates",
               attval     = "time latitude longitude altitude station_name",
               prec       = NA,
               verbose    = FALSE,
               definemode = FALSE )

    }

  if ("SNOW" %in% available_datafields) {
    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_snow,
              attname    = "standard_name",
              attval     = "thickness_of_snowfall_amount",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_snow,
              attname    = "cell_methods",
              attval     = "time: sum",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_snow,
              attname    = "description",
              attval     = "Daily Total Snowfall",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

      ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_snow,
              attname    = "coordinates",
              attval     = "time latitude longitude altitude station_name",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

  }

  if ("SNWD" %in% available_datafields) {
    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_snwd,
              attname    = "standard_name",
              attval     = "surface_snow_thickness",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_snwd,
              attname    = "cell_methods",
              attval     = "time: point",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_snwd,
              attname    = "description",
              attval     = "Snow Depth on Surface",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

     ncatt_put(nc         = nc_ghcn,
             varid      = netcdf_snwd,
             attname    = "coordinates",
             attval     = "time latitude longitude altitude station_name",
             prec       = NA,
             verbose    = FALSE,
             definemode = FALSE )

  }


  if ("WESD" %in% available_datafields) {
    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_wesd,
              attname    = "standard_name",
              attval     = "liquid_water_content_of_surface_snow",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_wesd,
              attname    = "cell_methods",
              attval     = "time: point",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_wesd,
              attname    = "description",
              attval     = "Liquid Snow Water Equivalent Depth on Surface",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

     ncatt_put(nc         = nc_ghcn,
            varid      = netcdf_wesd,
            attname    = "coordinates",
            attval     = "time latitude longitude altitude station_name",
            prec       = NA,
            verbose    = FALSE,
            definemode = FALSE )


  }


  if ("WSEF" %in% available_datafields) {
    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_wesf,
              attname    = "standard_name",
              attval     = "snowfall_amount",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_wesf,
              attname    = "cell_methods",
              attval     = "time: sum",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_wesf,
              attname    = "description",
              attval     = "Liquid Snowfall Water Equivalent",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

     ncatt_put(nc         = nc_ghcn,
            varid      = netcdf_wesf,
            attname    = "coordinates",
            attval     = "time latitude longitude altitude station_name",
            prec       = NA,
            verbose    = FALSE,
            definemode = FALSE )
  }


  if ("AWND" %in% available_datafields) {
    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_awnd,
              attname    = "standard_name",
              attval     = "wind_speed",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_awnd,
              attname    = "cell_methods",
              attval     = "time: mean",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_awnd,
              attname    = "description",
              attval     = "Mean Daily Wind Speed",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

     ncatt_put(nc         = nc_ghcn,
            varid      = netcdf_awnd,
            attname    = "coordinates",
            attval     = "time latitude longitude altitude station_name",
            prec       = NA,
            verbose    = FALSE,
            definemode = FALSE )

  }

  if ("AWDR" %in% available_datafields) {
    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_awdr,
              attname    = "standard_name",
              attval     = "wind_from_direction",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_awdr,
              attname    = "cell_methods",
              attval     = "time: mean",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

    ncatt_put(nc         = nc_ghcn,
              varid      = netcdf_awdr,
              attname    = "description",
              attval     = "Mean Daily Wind Origin Direction",
              prec       = NA,
              verbose    = FALSE,
              definemode = FALSE )

     ncatt_put(nc         = nc_ghcn,
            varid      = netcdf_awdr,
            attname    = "coordinates",
            attval     = "time latitude longitude altitude station_name",
            prec       = NA,
            verbose    = FALSE,
            definemode = FALSE )


  }






  ncvar_put(nc      = nc_ghcn,
            varid   = netcdf_lat,
            vals    = station_latitude,
            verbose = FALSE )
  remove(netcdf_lat,
         station_latitude)

  ncvar_put(nc      = nc_ghcn,
            varid   = netcdf_lon,
            vals    = station_longitude,
            verbose = FALSE )
  remove(netcdf_lon,
         station_longitude)

  ncvar_put(nc      = nc_ghcn,
            varid   = netcdf_alt,
            vals    = station_altitude,
            verbose = FALSE )

  ncvar_put(nc      = nc_ghcn,
            varid   = netcdf_stn,
            vals    = file_title_string,
            verbose = FALSE )

  remove(netcdf_alt,
         station_altitude)


  if ("TMAX" %in% available_datafields) {
    ncvar_put(nc      = nc_ghcn,
              varid   = netcdf_tmax,
              vals    = tmax,
              verbose = FALSE )
    remove(netcdf_tmax,
           tmax)
    }

  if ("TMIN" %in% available_datafields) {
    ncvar_put(nc      = nc_ghcn,
              varid   = netcdf_tmin,
              vals    = tmin,
              verbose = FALSE )
    remove(netcdf_tmin,
           tmin)
    }


  if ("TAVG" %in% available_datafields) {
    ncvar_put(nc      = nc_ghcn,
              varid   = netcdf_tavg,
              vals    = tavg,
              verbose = FALSE )
    remove(netcdf_tavg,
           tavg)
    }


  if ("PRCP" %in% available_datafields) {
    ncvar_put(nc      = nc_ghcn,
              varid   = netcdf_prcp,
              vals    = prcp,
              verbose = FALSE )
    remove(netcdf_prcp,
           prcp)
    }

  if ("SNOW" %in% available_datafields) {
    ncvar_put(nc      = nc_ghcn,
              varid   = netcdf_snow,
              vals    = (snow/1000.0),
              verbose = FALSE )
    remove(netcdf_snow,
           snow)
    }

  if ("SNWD" %in% available_datafields) {
    ncvar_put(nc      = nc_ghcn,
              varid   = netcdf_snwd,
              vals    = (snwd/1000.0),
              verbose = FALSE )
    remove(netcdf_snwd,
           snwd)
  }

  if ("WESD" %in% available_datafields) {
    ncvar_put(nc      = nc_ghcn,
              varid   = netcdf_wesd,
              vals    = wesd,
              verbose = FALSE )
    remove(netcdf_wesd,
           wesd)
  }

  if ("WESF" %in% available_datafields) {
    ncvar_put(nc      = nc_ghcn,
              varid   = netcdf_wesf,
              vals    = wesf,
              verbose = FALSE )
    remove(netcdf_wesf,
           wesf)
  }


  if ("AWND" %in% available_datafields) {
    ncvar_put(nc      = nc_ghcn,
              varid   = netcdf_awnd,
              vals    = awnd,
              verbose = FALSE )
    remove(netcdf_awnd,
           awnd)
  }


  if ("AWDR" %in% available_datafields) {
    ncvar_put(nc      = nc_ghcn,
              varid   = netcdf_awdr,
              vals    = awnd,
              verbose = FALSE )
    remove(netcdf_awdr,
           awdr)
  }

  nc_close( nc_ghcn )

  remove(nc_ghcn,
         netcdf_time_dim)

  print("--------------------------")
  print(paste("Station # ",
              ncdc_index,
              " of ",
              total_number_of_stations,
              sep = ""))
  print(filename_station_label)
  print(available_datafields)




  remove(Date,
         Days_from_1970_01_01,
         available_datafields,
         file_title_string,
         filename_ghcn_label,
         filename_station_label,
         fill_value,
         ghcn_station_code,
         ncdc_end_yymmdd,
         ncdc_start_yymmdd,
         netcdf_available_variables,
         output_file_name,
         ncdc_id_code,
         netcdf_output_file_name,
         station_name_label)



```